---
title: "Example of wrangling and plotting COVID-19 data"
author: "Cyrus Maz"
date: "07/04/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





```{r echo=FALSE, messages=FALSE, warning=FALSE, include=FALSE}
source("covid_R_tools.R")

```

```{r eval=FALSE}
source("covid_R_tools.R")
```


```{r}
cases_df=update_cases_df()
deaths_df=update_deaths_df()

country_names=c("Canada", "Australia", "Italy", "France", "Vietnam")

countries_cases=get_counts_by_country(cases_df,country_names)
countries_deaths_df=get_counts_by_country(deaths_df,country_names)

```


\newpage
# Logarithmic Chart of cases in Canada, Australia, Italy, France, Vietnam
```{r}
plot_log(countries_cases,lab="Cases")

```


\newpage
# Linear Chart of cases in Canada, Australia, Italy, France, Vietnam
```{r}
plot_linear(df=countries_cases,lab="Cases")
```


\newpage
# Logarithmic Chart of Deaths in Canada, Australia, Italy, France, Vietnam
```{r}
plot_log(countries_deaths_df,lab="Deaths")
```


\newpage
# Logarithmic Chart of Deaths in Canada
```{r}
plot_linear(df=countries_deaths_df,lab="Deaths")
```


\newpage
```{r}
country_name="Canada"
Canada_cases=get_counts_by_country(cases_df,country_name)

Canada_deaths=get_counts_by_country(deaths_df,country_name)


```


# Logarithmic Chart of Cases in Canada
```{r}
plot_log(Canada_cases,lab="Cases")
```


\newpage
# Linear Chart of Deaths in Canada
```{r}
plot_linear(Canada_cases, lab="Cases")
```


\newpage
# Logarithmic Chart of Deaths in Canada
```{r}
plot_log(Canada_deaths,lab="Deaths")
```


\newpage
# Linear Chart of Deaths in Canada
```{r}
plot_linear(Canada_deaths, lab="Deaths")
```

\newpage
# Get the provincial case/death counts 
```{r}
provinces_cases=get_counts_by_provinces(cases_df,country_name)
provinces_deaths=get_counts_by_provinces(deaths_df,country_name)

```


# Logarithmic Chart of Cases in Ontario, Quebec, and BC
```{r}
plot_log(provinces_cases,
         provinces=c("Canada_Ontario", "Canada_Quebec","Canada_British Columbia"), 
         lab="Cases")
```


\newpage
# Linear Chart of Cases in Ontario, Quebec, and BC
```{r}
plot_linear(provinces_cases,
            provinces=c("Canada_Ontario", "Canada_Quebec","Canada_British Columbia"), 
            lab="Cases")
```


\newpage
# Logarithmic Chart of Deaths in Ontario, Quebec, and BC
```{r}
plot_log(provinces_deaths,
         provinces=c("Canada_Ontario", "Canada_Quebec","Canada_British Columbia"), 
         lab="Deaths")
```

\newpage
# Linear Chart of Deaths in Ontario, Quebec, and BC
```{r}
plot_linear(provinces_deaths, 
            provinces=c("Canada_Ontario", "Canada_Quebec","Canada_British Columbia"), 
            lab="Deaths")
```

